Yoghurt under stress

### 2014-06-03 seminaire_Tanakalab.tex
Collaborators (Creep)

\institute[E.N.S. Lyon]{Ecole Normale Supérieure de Lyon}
\title[Yoghurt under stress]{Yoghurt under stress}
\author[M. Leocmach]{Mathieu Leocmach}
\date{1st June 2014}

@@

\AtBeginSection[]{
	\addtocounter{framenumber}{-1}
	\begin{frame}[plain]
		\tableofcontents[currentsection, hideothersubsections]
		{\footnotesize Leocmach \& Tanaka \textit{Nature Communications} 3, 974 (2012).}
	\end{frame}
}

@@

\begin{frame}{Fundamental issues in biogels}
\begin{itemize}
\item Linear elasticity in not well understood \textit{\scriptsize Gardel et al. Science 2004}
\item Strain and stress stiffening \textit{\scriptsize Storm et al. Nature 2005}
\item Fractures \textit{\scriptsize Bonn et al. Science 1998, Baumberger et al. Nature Material 2006}
\item Mechanical instabilities and morphogenesis \textit{\scriptsize Shyer et al. Science 2013}
\end{itemize}
\begin{block}{Our questions}
\begin{itemize}
\item What is the behaviour of a biogel under shear deep into the nonlinear regime?
\item What is the role of the solvent in mechanical instabilities?
\end{itemize}

\end{block}
\end{frame}

>>>>

\institute[E.N.S. Lyon]{Laboratoire de physique, Ecole Normale Supérieure de Lyon}
\title[Yoghurt under stress]{Yoghurt under stress}
\author[M. Leocmach]{Mathieu Leocmach}
\date{1st June 2014}

@@

\AtBeginSection[]{
	\addtocounter{framenumber}{-1}
	\begin{frame}[plain]
		\tableofcontents[currentsection, hideothersubsections]
	\end{frame}
}

@@

\begin{frame}{Fundamental issues in biogels}
\begin{itemize}
\item Linear elasticity in not well understood \textit{\scriptsize Gardel et al. Science 2004}
\item Strain and stress stiffening \textit{\scriptsize Storm et al. Nature 2005}
\item Fractures \textit{\scriptsize Bonn et al. Science 1998, Baumberger et al. Nature Material 2006}
\item Mechanical instabilities and morphogenesis \textit{\scriptsize Shyer et al. Science 2013}
\end{itemize}
\begin{block}{Our questions}
\begin{itemize}
\item What is the behaviour of a biogel under shear deep into the nonlinear regime?
\item What is the role of the solvent in mechanical instabilities?
\end{itemize}
\end{block}
\end{frame}

\section{Creep and yielding}

\begin{frame}{Merciless yoghurt breakers}

\begin{tabu}{X[c]X[c]c}
\includegraphics[height=0.3\textheight]{Chris}&
\includegraphics[height=0.3\textheight]{Thibaut}&
\includegraphics[height=0.3\textheight]{Seb}\\
Christophe Perge & Thibaut Divoux & Sebastien Manneville\\
PhD student & CNRS researcher & Professor\\
E.N.S Lyon &  CRPP Bordeaux & E.N.S Lyon\\
\end{tabu}

\end{frame}

\section{Wrinkling}
